---
title: "Yield comparison through cultivars"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Import

The first thing that should be done for the analysis is the package loading:

```{r setup}
library(stRawberry)
```

# Exploring using data visualization

In order to compare the yield of the cultivars, we should first create
some visualizations to explore the data a little bit better:

```{r}
diffPlot(
  var = prod,
  strata = cultivar,
  facet  = exp
  )
```

As we can see in the plot above, the Albion yield was visually
higher compared to the other two cultivars in the "Solo" experiment.
In the other experiments, this difference is much softer.

Now we can make use of the view via table. Using the `diffTable` function, we can check a summary of the characteristics of each experiment:

```{r}
# Create a list containing all experiments
experiments <- c("Solo", "Deitado", "Dupla", "Em pé")

# Run the table function for every experiment
purrr::map(
  experiments,
  diffTable
  ) %>% 
  purrr::set_names(experiments)
```

Thus, we verify that, in fact, the greatest difference in yield is shown within the "Solo" experiment.

# Modeling

After the previous visualization, we might want to verify the difference significance between Albion and the other cultivars in the "Solo" experiment. 

```{r}
diffAnalysis(
  var = "prod",
  experiment = "Solo"
  )
```

As can be seen from the output of the function, the cultivars, within the "Solo" experiment, all differ from each other in terms of yield.
